Placeholder

### 2021-02-05 Paper_Histograms.Rmd
Added COPING palette 9 and applied to GLAD/EDGI age prepan graph

@@

>>>>

COPINGpalette9 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73", 
                    "#FFED98",
                    "#BFD2EB", 
                    "#808080",
                    "#cccccc",
                    "3B47DA")

@@

##Age
###Prepan

```{r GLAD/EDGI age prepan}

GLAD.prepan %>% 
  ggplot(aes(x = age_category_collapsed)) +
  geom_bar(fill = COPINGpalette9) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Age distribution of the GLAD/EDGI prepan cohort",
       subtitle = paste("N =", dim(GLAD.prepan)[1]),
       x = "",
       y = "")
